ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-18 pyked.tex
add link to github proposal issue

In this paper, we presented the \ck{} data format for describing measurements
taken from fundamental combustion experiments, recognizing that the community
has a need for an open and standardized data serialization format. \ck{} files
are formatted using the YAML language and are plain-text, human- and
machine-readable, and easy to construct.

@@

\ck{} and \pk{} are currently under active development, and contributions from
the community are welcomed. All development occurs under the BSD 3-clause
license and the code is housed on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Future directions for development
are outlined in the public
roadmap\footnote{\url{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}}. The
highest priority issues are currently adding support for other types of
fundamental experiments, including flame speed, speciation, and flame extinction
measurements.

>>>>

In this article, we presented the \ck{} data format for describing measurements
taken from fundamental combustion experiments, recognizing that the community
has a need for an open and standardized data serialization format. \ck{} files
are formatted using the YAML language and are plain-text, human- and
machine-readable, and easy to construct.

@@

\ck{} and \pk{} are currently under active development, and contributions from
the community are welcomed. All development occurs under the BSD 3-clause
license and the code is housed on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Future directions for development
are outlined in the public
roadmap\footnote{\url{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}}. The
highest priority issues are currently adding support for other types of
fundamental experiments, including speciation in shock tubes, flame speeds,
and flame extinction measurements. We also welcome proposals for new experimental
types; see Issue \#60 in the \pk{} repository.\footnote{\url{https://github.com/pr-omethe-us/PyKED/issues/60}}
